### 2022-06-20 paper/Chapters/Chapter05.tex
add new model: fgcnn

>>>>

The inference result of guided-GCNN model is shown in Figure \ref{fig:ng-eval-synthetic}. With adding the information of a gray-scale image, the model is able to sharpen the details over the whole scene.

\begin{figure}[h!]
	\centering
	\begin{subfigure}[b]{0.19\linewidth}
		\includegraphics[width=\linewidth]{./Figures/ng-synthetic/fancy_eval_3_groundtruth.png}
		\caption{GT}
	\end{subfigure}
	\begin{subfigure}[b]{0.19\linewidth}
		\includegraphics[width=\linewidth]{./Figures/ng-synthetic/fancy_eval_3_normal_NG.png}
		\caption{g-GCNN}
	\end{subfigure}
	\begin{subfigure}[b]{0.19\linewidth}
		\includegraphics[width=\linewidth]{./Figures/ng-synthetic/fancy_eval_3_error_NG.png}
		\caption{Angle Error}
	\end{subfigure}
	\begin{subfigure}[b]{0.19\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_3_normal_GCNN.png}
		\caption{GCNN}
	\end{subfigure}
	\begin{subfigure}[b]{0.19\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_3_error_GCNN.png}
		\caption{Angle Error}
	\end{subfigure}
	\caption{guided-GCNN Normal Inference on Synthetic Dataset (object: dragon). GCNN result is shown on (d) and (e) as comparison.}
	\label{fig:ng-eval-synthetic}
\end{figure}

### 2022-06-20 paper/akweury/document.tex
add new model: fgcnn

The inference result of guided-GCNN model is shown in Figure \ref{fig:ng-eval-synthetic}. With adding the information of a gray-scale image, the model is able to sharpen the details over the whole scene.

\begin{figure}[h!]
	\centering
	\begin{subfigure}[b]{0.19\linewidth}
		\includegraphics[width=\linewidth]{./Figures/ng-synthetic/fancy_eval_3_groundtruth.png}
		\caption{GT}
	\end{subfigure}
	\begin{subfigure}[b]{0.19\linewidth}
		\includegraphics[width=\linewidth]{./Figures/ng-synthetic/fancy_eval_3_normal_NG.png}
		\caption{g-GCNN}
	\end{subfigure}
	\begin{subfigure}[b]{0.19\linewidth}
		\includegraphics[width=\linewidth]{./Figures/ng-synthetic/fancy_eval_3_error_NG.png}
		\caption{Angle Error}
	\end{subfigure}
	\begin{subfigure}[b]{0.19\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_3_normal_GCNN.png}
		\caption{GCNN}
	\end{subfigure}
	\begin{subfigure}[b]{0.19\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn-synthetic/fancy_eval_3_error_GCNN.png}
		\caption{Angle Error}
	\end{subfigure}
	\caption{guided-GCNN Normal Inference on Synthetic Dataset (object: dragon). GCNN result is shown on (d) and (e) as comparison.}
	\label{fig:ng-eval-synthetic}
\end{figure}

>>>>

From the Figure \ref{fig:normal-histo-diff} we can observe the normal difference between ground-truth and GCNN predicted normals in another dimension. It separates the interval \left[ -1,1 \right], which is exactly the range of normal vector, to 256 sections. Then it counts the number of points locates in each section for 3 axes.  The 3 axes are fitted quit well in most of interval but other than \left[ -0.25,0.25 \right] for x and y axes and  interval close to $ -1 $ for z axis. Therefore a further constraint can be considered to the loss function related to the normal difference shown in this figure.

It is faulty that almost no normal has -1 z-component in GCNN predicted normal map. The reason?
\begin{figure}[h!]
	\centering
	\includegraphics[width=\linewidth]{./Figures/normal-histo-diff/normal-histo-diff.png}
	\caption{The normal difference of between GCNN and ground-truth in x, y, z-axis respectively. The y axis indicates the number of points, x axis indicates the value of normal in x/y/z axis. (The chart is based on the "dragon" scene showing above)}
	\label{fig:normal-histo-diff}
\end{figure}
